---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

# assess

assess: Course assignment grader for courses taught by Professor John Paul Helveston.

This package is highly bespoke to the [courses](https://www.jhelvy.com/teaching) taught by Professor John Paul Helveston at George Washington University. It is not necessarily designed for others to use (there isn't much careful documentation, at least for now), but you're welcome to use it if it's helpful for you!

## Installation

The current version is not yet on CRAN, but you can install it from
Github using the {remotes} library:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("jhelvy/assess")
```

Load the library with:

```{r, eval=FALSE}
library(assess)
```

## Author, Version, and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- Date First Written: *Saturday, Dec 10, 2022*
- License: [MIT](https://github.com/jhelvy/assess/blob/master/LICENSE.md)
